Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-07 tests-onezonecollapse.tex
Minor note to emphasize we're not using constant gamma.

The one-zone collapse test simulates the collapse of a
self-gravitating gas cloud using a semi-analytic model for the
evolution of gas density and adiabatic heat input as a function of
time.  It is designed to test the chemistry and cooling modules over a
wide range in densities and over physically motivated timescales.
Because this test disables the hydrodynamic and gravity solvers and
uses a simple model for the density evolution, it is far faster than
running a true collapse simulation.  The density evolution is based on
the self-similar Larson-Penston \citep{1969MNRAS.145..271L,
1969MNRAS.144..425P} solution for isothermal collapse with a
modification to account for the efficiency with which the heat
introduced by compression can be radiated away
\citep{1983ApJ...265.1047Y}.  Our implementation, described briefly
here, follows the work of \citet{2005ApJ...626..627O}, and we direct
the interested reader to this paper for further details.  The
evolution of the gas density, $\rho$, is given by

@@

where $\Lambda$ is the cooling rate in units of erg s$^{-1}$ g$^{-1}$
and energy, temperature, density, and pressure are related by the
ideal gas law.  Figure \ref{fig.onezone} shows an example of the
one-zone collapse test performed with an initial number density of 1
hydrogen atom per cm$^{-3}$ and an initial temperature of 100 K using
the 12 species chemistry network with H, D, and He species and metal
cooling rates calculated with the \texttt{Cloudy} code.  The effects
of metal cooling can be clearly seen; as the metallicity increases
from zero to $10^{-2}$~Z$_\odot$, the gas rapidly and significantly
deviates from the primordial result (black line).  Our primordial
results compare very well to those shown in
\citet{2005ApJ...626..627O}; however, we use a different metal cooling
method, so the lines describing the evolution of the
metal-enriched gas are not directly comparable.

>>>>

The one-zone collapse test simulates the collapse of a
self-gravitating gas cloud using a semi-analytic model for the
evolution of gas density and adiabatic heat input as a function of
time.  It is designed to test the chemistry and cooling modules over a
wide range in densities and over physically-motivated timescales.
Because this test disables the hydrodynamic and gravity solvers and
uses a simple model for the density evolution, it is far faster than
running a true collapse simulation.  The density evolution is based on
the self-similar Larson-Penston \citep{1969MNRAS.145..271L,
1969MNRAS.144..425P} solution for isothermal collapse with a
modification to account for the efficiency with which the heat
introduced by compression can be radiated away
\citep{1983ApJ...265.1047Y}.  Our implementation, described briefly
here, follows the work of \citet{2005ApJ...626..627O}, and we direct
the interested reader to this paper for further details.  The
evolution of the gas density, $\rho$, is given by

@@

where $\Lambda$ is the cooling rate in units of erg s$^{-1}$ g$^{-1}$
and energy, temperature, density, and pressure are related by the
ideal gas law, including effects from molecular hydrogen as appropriate.
Figure \ref{fig.onezone} shows an example of the one-zone collapse test
performed with an initial number density of 1 hydrogen atom per cm$^{-3}$ and
an initial temperature of 100 K using the 12 species chemistry network with H,
D, and He species and metal cooling rates calculated with the \texttt{Cloudy}
code.  The effects of metal cooling can be clearly seen; as the metallicity
increases from zero to $10^{-2}$~Z$_\odot$, the gas rapidly and significantly
deviates from the primordial result (black line).  Our primordial results
compare very well to those shown in \citet{2005ApJ...626..627O}; however, we
use a different metal cooling method, so the lines describing the evolution of
the metal-enriched gas are not directly comparable.
